An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-27 draft.tex
Updates biblio and writes state of the art refs #2

\section{State of the Art} 
\label{soa}
% a lot of this has been done in the previous method... Maybe there's
% not that much to do - JJ
% Hadoop 
%     Comparison \cite{ferrucci2018using}
%     Hadoop\cite{fazenda2012} 
%     FlexGP \cite{FlexGP}, 
%     elephant56 \cite{salza2016elephant56},

>>>>

\section{State of the Art} 
\label{soa}

Although on first sight containers look like simply a method that
allows easy shipping of applications, they are much more than
that. One of the first features that make them interesting is their
ephemerality: fast startup and teardown time make them usable for
machine-independent and cloud deployment of simple, ephemeral and
maybe stateless functions. On the other hand, containerization also
allows, through the use of orchestration engines like Docker Swarm or
Kubernetes, or through simple, non-self-scaling specifications using
Docker Compose, a definition of all the relationships between
different parts of the application, or services. The full realization
of Docker-based architectures has led to the creation of a series of
patterns that, together, conform cloud-native application development
\cite{kratzke2017understanding}.

However, in the field of evolutionary algorithms, this has been a slow
realization, from the origins where Salza and Ferrucci
\cite{salza2016approach,salza2016develop} proposed an architecture
that carried evolutionary algorithms to the cloud, developed further
in \cite{de2017parallel} which starts to introduce cloud native
aspects such as the use of messaging queues and CoreOS as an operating
system designed from the ground up for container utilization. The way
these containers are organized, however, is rather classical in
nature: a master-worker approach, communicated using RabbitMQ, where
replicated workers perform the tasks in parallel. They called their
approach AMQPGA, inspired by the protocol, AMQP, used by RabbitMQ, the
messaging system. Other EAs topologies have also been used in the
cloud: \cite{dziurzanski2020scalable} adapts an island model to a
container architecture, in a system that is functionally equivalent to
classical models, but with the added advantage of being easy to deploy
and run.

Later approaches use microservices \cite{khalloof2018generic}, or were
systematized \cite{salza2019speed} achieving speed-up through the
creation of an abstraction layer over the evolutionary algorithm
services, and also automatization of the whole workflow. This research
bumped into some problems, since speedup is limited, mainly due to the
non-automatic scaling of services and also the presence of a single
master which is the one that runs the evolutionary
algorithms. However, this master-worker architecture can be turned
around with other kind of evolutionary architectures, such
as pool-based systems
\cite{valenzuela2015implementing,merelo2012sofea,sofea:cec2012} where
a better match to the inherently heterogeneous nature of cloud-based
architectures. Pool-based systems are closer to serverless systems
\cite{malawski2017serverless}, and they pull from the pool and run
whole algorithms, instead of just evaluation. The pool from where they
pull is the common store of results, and can be accessed in an
asynchronous way, which suits better the nature of cloud systems.

% a lot of this has been done in the previous method... Maybe there's
% not that much to do - JJ
% Hadoop 
%     Comparison \cite{ferrucci2018using}
%     Hadoop\cite{fazenda2012} 
%     FlexGP \cite{FlexGP}, 
%     elephant56 \cite{salza2016elephant56},
